Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-03 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:03	19:02:18	(Mon 3.Aug)
la2pdf commit - 2015:08:03	19:38:08	(Mon 3.Aug)

\begin{itemize}
\item \emph{Window function}. Studies of typical MVDR responses for shadow, speckle and highlight regions in an image.
\item \emph{Window parameters}. 
\end{itemize}

@@

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{Window parameter boundaries. LCA images using an oversampled image and a relatively large window database with $N_\beta=20$ window types, each steered $N_\phi=19$. }\label{oversampling_mosaic_bounds}
\end{figure*}

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

>>>>

\begin{itemize}
\item \emph{Window function}. A Kaiser window was chosen due to its resemblance to typical MVDR responses for shadow, speckle and highlight regions in an image, as shown in \Fig{mvdr_selected_windows}.
\item \emph{Window parameters}. The Kaiser window parameter $\beta$ tunes the compromise between resolution and sidelobe suppression. At $\beta=0$ ) and a gaussian curve (
\end{itemize}

@@

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds.pdf}%
\caption{Window parameter boundaries. LCA images using an oversampled image and a relatively large window database with $N_\beta=20$ window types, each steered $N_\phi=19$. }\label{oversampling_mosaic_bounds_beta}
\end{figure*}

\newpage
\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.5\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

hmm
